\chapter{Literature Review}

\section{Introduction}
For security market analysis, there’s a requirement to develop new tools that in combination with ancient prediction models can tune the predictions by taking into consideration factors that don’t directly have their origin within the company itself, however the final public’s perception of the market and opinions of the studied stock especially. a trial to extract additional information from a dataset of tweets was conducted and therefore the chance to acquire higher stock value prediction with a restricted-sized knowledge. The aim of this work is to push a machine learning approach with deep learning to unravel this downside. Typically, once a machine learning model isn’t correct enough, it may be solved by coaching it with a bigger dataset. Earlier analysis has used solely volume and follower count. This work extends their findings to check the performance of stock predictions with a machine learning model, using tweet attributes. For prognostication stock market expression and costs progression which have been learned respective vestibule in literature. We studied some works which are focused on developing the process of prediction situated on sentiment analysis of random news or random tweets post both worked on stock costs. Another target on stock market price prediction using several time frames. Furthermore, particular research methods demonstrated that works were a vigorous correlation interpolated stock market prices changing with random twitter posts and both researchers used different formulas or different algorithms. Microblogging has been spreading online and lots of researchers have shown their interest in this means of human reactions for almost 10 years. Due to its capability to transmit concepts across individuals, a quest identifies it as on-line spoken disapproval. Twitter has fairly often been thought about as the foremost simple alternative by researchers for sentiment analysis and opinion mining on microblogging knowledge. Indeed, it provides a large volume of narrow-minded knowledge on a really broad variety of subjects and encompasses a free API for creep. Tweets and users.\\

Siersdorfer et al. \cite{siersdorfer2010useful} proposed that a small number of researchers who have percolated sentiment analysis of social networks such as Twitter and YouTube \cite{sureka2010mining}, \cite{siersdorfer2010useful}, \cite{cheong2011social}. In dispersion through the above mentioned, the elbow grease which is uttermost in conjunction with affiliate. The researchers who are hypothesized innumerable 6 million comments, which are self-possessed from 67,000 YouTube videos to pick-out the consensus in the thick of comments, views, comment ratings and topic categories. The authors panoply betrothal repercussions in prognosticate the comment appraisal of new modish comments by physique divination models practicing by the time mentioned scaled comments. Nonetheless, the meticulousness of sentiment apportionment inclines condensed of the accuracy of run-of-the-mill topic-based text categorization which mileage such machine learning techniques. Another Pronounced work in sentiment analysis is by Bollen et al. The authors used two sentiment hunting paraphernalia flawlessly crystal-ball divine the circadian reconstruction to the closing scruples of the Dow Jones Industrial Average (DJIA) and Index the Twitter feeds of users. The authors calculate an accuracy of 86.7\% and a shrinkage of more than 6\% in the mean average percentage error. Our work bears no resemblance intrinsically from the top of the whole shebang.\\

Nir. B. et. al \cite{benevenuto2008identifying} proposed sentiment analysis that clenched weighing text of frame to take sentiment scores for articles. They primarily deleted pull up words before making up data structure from body text of body. Then they built a verdict TextBlob library. Textblob is made on origin in python of the NLTK package7 and grasped for an array of fiction articles to use as a probable tool. Working a lexicon basically foregoing dictionary of contentions-based dictionary supported path at any time, confidential based their polarity values, to count the polarity score of word of a section stunt word Textblob, their python tool obtained proscribe away of a bit of scripting to benefit a packet of texts way to arrive to the sentiment polarity scores. Those scores were to reach the variance of -1 to 1, where-1 defines an intensely negative article although 1 defines a positive article. The scores which were assembled and gripped on in a strikingly learning of pandas frame well-organized with the highlight line of article, the text calculate and hence the parts of the above mentioned works which are permeated to subsequently of large amount of whole, they collated the previous polarity price learning frames for yearly block of news works.\\

An. Mt. and Al. Mi. \cite{bhandari2017stock} et. al wrote that Sentiment analysis was a significant portion solution. In their article, they used four mood parts, such as Calm, Happy, Alert, and Kind. Then they demonstrated a few typical tools such as Opinion Finder, Sent Wordnet etc. searched them deficient, incomplete and hence determined their own analytical code to improve.\\

Ar. K., Jo. Za. and San. Krs. \cite{mittal2012stock} et. Al proposed that an opinion is well-advised such as a packet of free words. The positive and negative opinions in the suite dataset which are reserved in two partition lexicons, that they excerpt to such as positive lexicon (positive opinions) and negative lexicon (negative opinions). For every opinion, every text is counted the digit of times the word by calculating and the polarity or sentiment arrives in the positive and negative score. Every text, the polarity that is the positive number of times the word issues on a positive score divided by the whole number times that exposes both positive and negative scores.\\

Ai .V and Dr. Vani Priya \cite{krishna2013polarity} et. al proposed that Twitter is passed down on the point of a actual time which confesses people to exchange their surveys, depicts their inquiring mind, regards or inference just as to how they find around any item and imply with brief messages or sectional realm of text tell that constitute of sacralizing service pulpit of 140 characters or less than. Twitter is an excellent data source to be considered for sentiment analysis for predicting stock values. So, brings to tweets from Twitter API, first needs to register an App over their twitter account and specify an application. To follow the steps and then follow to get to the link (\href{https://developer.twitter.com/en/apps}{https://developer.twitter.com/en/apps}) and achieve the APIs. Dev Shah et al. \cite{nemes2021prediction} et. al had learned about twitter data from twitter newsfeed and applied sentiment analysis on the news. This paper they had discovered polarity for the pharma sector and on the whole their main focus was on the stock's cost ups and downs that was situated on the polarity bookwork.\\

Another paper written by Du Peng \cite{shah2018predicting} et. al mostly learned the market vaporousness and also created the sentiments of people and to identify the relation. \\

Vai. Gururaj, Shr. V R and Dr. As. K. \cite{peng2019analysis} et al. proposed that here one in all ways used the $p = mr + q$ equation to suit a flat-out line for structure: a sketch such as row occurs of points of the given dataset via the most number. After that, a right away line per the dots such a group of the intervening within every drop and consequently the series is least, using mathematical terms, to plot rate of the dataset on an epistle. To call the hypothesis is able to predict the $y$ value for any given $x$ and this prediction technique is mentioned in rectilinear regression and hence the process conducted using the youngest volume squares method. The method is extensively owned by statisticians, availed simultaneously the initial notion of ML. The hypothesis function of rectilinear regression formation in total,\\

\begin{equation}
     p = t\theta(r) = \theta_0+\theta_1r 
\end{equation}

comment that is mostly similar to the line equation. $\theta$0 and $\theta$1 is conferred to $\theta$ $t(x)$ to inspire the inventory output $p$. The validity of their hypothesis is a cost function applying of magnitude, that is, a mean of every result with inputs from $r$ is parallel to exceptional output $p$ is of the hypothesis \\

Yahya Eru Cakra and Bayu Distiawan Trisedya \cite{cakra2015stock} et al. proposed that Linear regression is that model which is used regression method to be used for classifying numerical class that is created linear function by enumerating weight values ($\omega$) for each feature (β). The function can be written as be subsequent to,\\

\begin{equation}
     x = \beta_0\omega_0+\beta_1\omega_1+... .+\beta_n\omega_n
\end{equation}

 X are regression values for example to data. Plethora methods to estimate a linear regression model which cut out of ultimate data has a normal distribution in its enduring. At the edge of, it can be in conjunction with appraised by stretching toward at the coefficient of single-mindedness value $(R^2)$. $R^2$ which is the square of the coefficient of correlation $(R)$ that is between approximated values and real values. $R^2$ magnitude from 0 to 1. The more $R^2$ value close to 1 is the over and above data which is adapted.The coefficient of indomitability which is the lagniappe of the full amount contradicts distinction in the tied to apron strings variable which can be calculated by departure from the norm in the independent variable(s). After that $R^2$ is + 1, there endures a put finishing touch on linear interrelation between $p$ and $q$, i.e 100\% of the variation in $q$ is elucidated by variation in $p$. Meanwhile this is $0< R^2 <1$, that is an insubstantial linear consanguinity in the thick of $p$ and $q$. \\
 
U. Pr. Gur. and S. K. et. al. \cite{gururaj2019stock} wrote that they used the Dow Jones index flush smallest dot of the year during 21\% to date or 39\%. They cut down 3 months considering the Dow Jones shocked slag sole to return to its previous vertex.David Valle‑Cruz ,Vanessa Fernandez‑Cortez, Asdrúbal López‑Chau and Rodrigo Sandoval‑Almazán et. al.\cite{valle2021does} used Investor sentiment could potentially predict the direction of indexes a few days ahead of time. During the COVID-19 epidemic, markets took 0 to 10 days to react to information published and distributed on Twitter, according to this analysis. This period ranged from 0 to 15 days during the H1N1 pandemic.  They discovered correlations not only in the positive but also in the negative shift values (from 11 to 1). This suggests that the stock market's performance influences Twitter users' reactions. This took 1 to 11 days in the case of H1N1, and 1 to 6 days in the case of COVID-19.\\

Chetan Gondaliya, Ajay Patel2 and Tirthank Shahthe \cite{gondaliya2021sentiment} et. al. used Logistic Regression and Support Vector Machine algorithms which have produced better results, making these two algorithms superior in sentiment prediction when using the Bag-of-words technique. The study makes a substantial contribution to the identification of superior algorithms for sentiment prediction in terms of accuracy and gives a strong platform to evaluate six selected algorithms with special reference to Indian stock market news and covers the most recent time period of Covid-19 pandemic impact, as natural language processing becomes a more powerful tool for interpreting text messages. In an additional study performed by Wang, X., \& Luo \cite{wang2013sentimental} et. al. employing sentiment analysis to forecast movie performance based on data from social networking sites. They gathered sentiments from Twitter and YouTube, among other social media platforms. The K-means clustering technique was used to predict the outcome of the film. In further study by Aditya Bhardwaja, Yogendra Narayanb , Vanrajc , Pawana and Maitreyee Duttaa et. al.\cite{bhardwaj2015sentiment} employed the Python scripting language, which has a quick execution environment, to assist investors in predicting where their money should be put in the stock market. They also did not reach their desired goal.\\

Papadamou, Stephanos and Fassas, Athanasios and Kenourgios, Dimitris and Dimitriou et. al. \cite{papadamou2020direct} wrote that the risk-aversion channel of pandemic spread in the stock market, as well as the attention-induced price pressure hypothesis, are both supported by our findings. As a result, our findings add to earlier research that shows how investor attention in a "google" or "internet" oriented economy affects implied volatilities in stock markets. These findings reveal an investor sentiment channel that grows as a result of behavioral biases during pandemic crisis periods, providing useful information to investors and policymakers.Understanding the links between investors' decisions on a pandemic and asset price volatility is crucial for creating and executing market and economic policy actions.


\section{Research Gap}

V Kranthi Sai Reddy et. al\cite{reddy2018stock} proposed SVM algorithm works on a big dataset value that is collected from different worldwide financial markets, and it proposes the use of data collected from multiple global financial markets with machine learning algorithms in order to anticipate stock index movements. The main problem with the work is that overfitting is not an issue while using SVM. Various machine learning-based models are currently being presented for predicting the daily movement of market equities, with numerical results indicating a high level of efficiency. Linear regression, on the other hand, is a model that is used to enhance a well-trained predictor. Compared to the chosen benchmarks, the model yields a bigger profit. Thien Hai Nguyen and Kiyoaki Shirai et. al.\cite{nguyen2015topic} suggested a TSLDA-based approach for predicting stock price movement based on social media sentiments. Although the proposed method's accuracy of 56 percent is not particularly great, the results can be satisfactory, as evidenced by prior works.However, one disadvantage of TSLDA is that it requires you to specify the number of subjects and emotion ahead of time.To overcome this, a model known as linear regression is a non-parametric topic model that estimates the number of topics present in the data.

P. K. Singh, A. Sachdeva, D. Mahajan, N. Pande, and A. Sharma et. al.\cite{singh2014approach} wrote that Sentiment analysis was used in a recent study to filter out unnecessary reviews on popular e-commerce platforms. MongoDB was used to store results for unstructured data in the backend of their study. This is an old method of gathering data and performing sentiment analysis. on the other hand, using sentiment analysis on Twitter trending topics, has proven to be quite effective. Aishwarya .V  and Dr. Vani Priya et. al. \cite{prasadinternational} experimented that There are a few things to consider: Sentiment Analysis focuses on using context, tone, and other criteria to forecast stock values and people's opinions in tweets. They developed TextBlob, a model that processes live tweets and categorizes them as good, negative, or neutral, based on Twitter data.This trained model then forecasts stock market rates.They did note, however, that the ratio of negative tweets is substantially larger, and that the results would be less accurate, hinting that the emotion of the people they analyzed isn't totally accurate.
Sandipan Biswas, Prasenjit Das, Rajesh Bose and Sandip Roy et. al.\cite{biswas2020examining} explained the impacts of a pandemic were studied using real-life examples of the effects of coronavirus infections over the world.They studied a variety of news stories with numerical values in order to better comprehend stock market trends based on previous patterns.They also took into account the ideas and opinions expressed by share reviewers. The opinions of reviewers have an impact on traders who invest in the stock market.Their work has some flaws, such as the use of aggregated share prices and the lack of daily news and articles gathered from different financial and stock market websites.
Our work differs from the previous work in a few ways; now we may give a brief description of it.We begin by downloading stock market data in a csv file from Yahoo Finance and organizing it intelligently. Then it may be used to generate price average orders using DJIA values, sentiment analysis in Twitter random posts piece by piece, and convincingly forging linear regression for prediction.As a result, we use textblob to collect random tweets for sentiment analysis. We noticed that a big amount of text-file data had been circulating and had shown to be beneficial to researchers.Then, using the Twitter API, acquire random twitter data as well as random twitter postings, clean twitter datasets, then perform TextBlob sentiment analysis to these cleaned datasets.TextBlob assesses and ranks positive, negative, and neutral text.Then calculating the perfect percent of sentiment.Prediction using linear regression.Furthermore, we establish a point of convergence on the transformation in the progression of users' (commenters') attitudes in ancient history over time, as well as the implications of the posts (queries based on different keywords)Linear regression can minimize squared errors and can be used in input-output training data sets.\\