\chapter{Conclusion and Future scope}
Using data from Yahoo Finance, this research constructs a model and algorithm for stock price prediction. Traders, investors, and analysts benefit from efficient and accurate stock price prediction systems since they provide helpful information such as the stock market's future direction. For the best accuracy, we discovered that historical data should be used for Linear Regression. Data scientists' possibilities for solving fascinating problems with high accuracy are expanding thanks to deep learning technologies. We used a large scale collection of tweet data to uncover links between Twitter-based sentiment analysis of a particular company/index and its market performance in this article. Our findings reveal that negative and positive aspects of public mood have a strong cause-and-effect relationship with individual stock/index price changes. We also looked into how prior week sentiment features influence the opening and closing values of stock indexes for various tech businesses and important indexes such as the DJIA and NASDAQ-100.Our findings are in some ways similar, but there are some significant variances. To begin, our findings reveal a stronger association between negative and positive mood dimensions and DJIA values, as opposed to their findings, which showed a strong correlation with only the good mood dimension. Second, while we were unable to achieve a high percentage result of 87 percent, our 73 percent result using Linear regression provides better proof that the connection exists over the full data set.\\



Finally, numerous factors are left out of our analysis. To begin with, our dataset does not represent true public mood; it only takes into account persons who use Twitter and speak English. When the actual mood is analyzed, it is feasible to establish a higher correlation. The association could be explained by the fact that people's moods influence their financial decisions. However, there is no clear link between persons who invest in stocks and those who use Twitter more regularly, however there is an indirect link: people's investment decisions may be influenced by the emotions of those around them, i.e. general public attitude. All of these will continue to be investigated in the future.\\