\chapter{Introduction}
\section{Background}
Almost two and a half trillion stock investors within the world per 2021 recent statistics are contributing to global economics through the exchange. The overall global stock market trading turnover is around \$95 trillion. Particularly, retail investors have made a buy or sell investment decisions depends on the world situation. Within the whole world, there are plenty of taking resolutions for an investment to involve an outsized volume of cash are produced. Spending a lot of time on uncovering funding lucky chances by retail shareholders has become a day-to-day difficulty. On the other hand, other investors are looking for white-collar commercial advisory services, the prices are sky high only for retail shareholders. For this reason, they are not being able to take that service easily as others and have to make all types decision depending on their own market analysis. So, this type of doing own analysis is becoming very tough in this modern time when there are a lot of technological opportunity.\\

Humans are being sophistical in their behavior at some certain events or matters. While not being valued, task based different thinking, choices get biased by psychological feature biases or personal emotions, resulting in gratuitous losses. The analysis of the company’s shares is currently obsessed with most on completely different social media sites. Among different social media sites that has most significant among the economic and share market empire is Twitter. Almost 500 million tweets are sent by active users on a usual. To express their various emotions through these tweets, which are being translated into helpful info. At now, such an improbable quantity of social media knowledge can’t be entirely accumulated by investors only being alone. It is a just about not possible task for them to make it on their own. Therefore, a processed analysis system is vital for investors, because this system can mechanically appraise stock trends victimization such giant amounts of knowledge in our worked database.\cite{bhavya2021stock}\\ 

Without access to quantitative and information-pushed models on people’s sentiment analysis, one apparent technique retail buyers could use to wager the market is through simple signs, as an example, easy regression and exponential shifting average. Again, there are huge up-downs in the world stock market for last years, due to coronavirus and for it's post covid impact. Like an example, the stock market came crashing down suddenly because of sudden attack of coronavirus and also the finance instability. This crash because caused a huge fall down to the market and after two months again tried to enter at the stock markets, which continued through at the end of the same year. Another noticed matter is when in 2019 the leading company was Microsoft, but in the middle of year 2020, Arabian oil company took the leading which was worth around \$1.36 trillion.\\

To get the analysis of the above information and also for closing prediction of stock prices there have been a lot of experiments caused in these recent years. Supervised learning and unsupervised learning classifications of machine learning models are used consequently to predict the stock prices with the most accurate level. Among those several techniques like the Decision Tree method, Support Vector Machine, KNN, Random Forest method, Naive Bayes method, Logistic Regression are vastly used to apply machine learning model for better prediction. Without these techniques, R programming is also used to plot the data of analyzing and also future prediction.\\

Again, retail investors will be able to predict the stock exchange by drawing a regression line that connects the utmost or minimum of possible prices. A regression system is used to guess and predict the current market trend which is inspired by the adding modern machine learning algorithms for research, these algorithms might serve as implicit tools to seek out actual patterns within the trend of stock prices, this information may be useful to supply redundant perceptivity for retail investors when making different investment planning.\\

Twitter sentiment analysis is an imperial of data and can hand over intuition that can intimate positive or negative discern on stocks and direction. There has an enough number of research on sentiment analysis on different topics, just for movie reviews and Twitter post in random or defined days, months. In this work we use sentiment analysis on twitter random posts. Saving Twitter Sentiment Analysis for implementation by applying twitter API kept by twitter. This method is extirpating tweets from twitter in given below :\\

\begin{itemize}
    \item Firstly, import essential packages and libraries.
    \item Determine criterion which build up relationship with twitter API. 
    \item By removing some words for cleaning the tweets.
    \item Tokenize every phrase withinside the dataset and keep it into the dataset
    \item For every word to compare with positive or negative.
    \item Finally, Find the sharpness of positive, negative and neutral tweets.
\end{itemize}


\section{Overview}
The study is going to connectivity bounded by the recent timeline from 2020 and the stock market of research. In this study, we use sentiment analysis for prediction stock market ups-downs and also use tweeter data that is taken from Twitter. We propose here a completely unique topic modeling throughout sentiment scoring methods. Our proposed model has been designed to function as a number one indicator to serve in recession prediction models. The work is predicated on our hypothesis that includes such a sort of sentiment indicator, with unstructured data aggregated from Twitter trending posts, shall be significant in improving prediction capabilities. As such, derivations made up of unstructured data collected and collated from Twitter posts using Twitter API to supply a measure of the polarity of the type of data that both producers and consumers encounter. Through our research, we demonstrate text sentiment analyses tools while, at an equivalent time, presenting our design for a replacement time-series measurement of economic sentiment. Our data is extracted from yahoo finance DJIA’s historical data between March 1, 2020, till now. We undertake comparisons for estimating predictive accuracy of several sentiment analysis models using Twitter data that are posted either as being positive or negative by humans which can almost fall down or up the Dow Jones Industrial Average (DJIA).\\


\section{Problem Statement}
\begin{itemize}
    \item Some researchers explored correlation between sentiments of twitter and stock indices but they were unable to meet the main goal.
    \item For the social network graph, a data visualization tool such as NodeXL was utilized to visualize the result of user's opinion.
    \item In previous research, presented a Machine Learning (ML) approach that taught using publicly available stock data to build intelligence. In this respect, the study employed a machine learning technique known as Support Vector Machine (SVM) to predict stock prices for large and small capitalizations, as well as in three separate markets, using daily and up-to-the-minute prices.
    \item In foregoing paper, presented a hybrid technique that combined an LSTM network with a genetic algorithm (GA), they used daily Korea Stock Price Index (KOSPI) data to test the proposed hybrid strategy. 
    \item To establish the relationship between "public sentiment" and "market sentiment “using sentiment analysis and machine learning concepts and validate their findings, present a new cross validation method for financial data and use SOFNN to achieve 75.56 percent accuracy on Twitter feeds and DJIA values.
\end{itemize}


\section{Motivation}
The final aim of our work is attending to distribute buyers in the act of any type of important event stab mechanism that makes use to assist the rapid-changing by voyaging stock market of using machine learning. The study pursuits to socialize and open up today’s system by getting to know technologies for retail traders. Apart from the models which tried to decrease, exceptional finance-particular rankings are added to segregate and figure out the overall achievement of conflicting systems, especially version accuracy rating, version trend score, and stock purchase or promote rating. The ratings also are constructed to bring important and consequentially words to assist buyers to apprehend inventory and make funding decisions.\\


\section{Objective} 
This proposed system will serve the following objectives :
\begin{itemize}
    \item To propose a novel topic modeling accompanied by sentiment scoring methods, designed to function as a leading indicator, and to serve in recession prediction models.
    \item To construct a model having reduced complexity and higher accuracy.
    \item To create this model, an appropriate algorithm text blob was used to predict sentiment.
    \item To assemble as an additional perceptible contraption for investors from a unique mindset with the assist of the era they’ll be looking for better statistics in peer the market.
    \item A large mess that can give over data with profitable predictions in contrast to public opinion to a suitable circumstance, despite the fact that each tweet is irrelevant to the point of a section.

\end{itemize}


\section{Research Outline}
Our study is divided into four sections with different sub-sections and also demonstrated the required figures into it. In chapter II, we have discussed related works in this area and which and how the model was used in those studies with proper explanation. Also, we tried to cover the gap between those papers which might be done better for doing the appropriate research. After that, we have briefed our own system model with the required algorithms and figures to better understand and also got the result after applying the machine learning technique in chapter III. Last but not the least, we concluded with our future work by discussing its possible scope and betterment in chapter IV.\\